---
title: "Linear Model Prediction"
author: "Racheal Adeneye"
date: "2025-05-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
require(knitr)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt", sep="", header=TRUE)
```

### Model 1: SIMS~ARM
```{r}
basiccNN <- ggplot(data,aes(y=SIMS,x=ARM))
```

```{r}
basiccNN + geom_point() + ggtitle("SIMS vs ARM")
```

As we can see in the scatter plot for SIMS vs ARM above, we can see that the data is going uphill to the right. This relationship is a positive relationship.

### Numerical Results
```{r}
cor(SIMS~ARM, data=data)
```

The correlation between SIMS and ARM is 0.69.

### Inferential Results
```{r}
model1 <- lm(SIMS~ARM, data=data)
summary.lm(model1)
```

Out adjusted R-squared value is 0.467 and our p-value is extremely small.

### Target Dataframe
```{r}
target <- data.frame(ARM=90, GRIP=90)
```

```{r}
predict(model1, target, interval=c("prediction"))
```

The prediction interval goes from -1.6 to 3.2.

```{r}
predict(model1, target, interval=c("confidence"))
```

The confidence interval goes from 0.59 to 1.

```{r}
armmod <- lm(SIMS~ARM, data=data)
plot(SIMS~ARM, data=data)
abline(armmod)
summary.lm(armmod)
```

### Model2 SIMS~GRIP
```{r}
basiccNN2 <- ggplot(data,aes(y=SIMS,x=GRIP))
```

```{r}
basiccNN2 + geom_point() + ggtitle("SIMS vs GRIP")
```

In this plot as well, we see that the data is going uphill and to the right. This relationship is a positive relationship.

### Numerical Results 2
```{r}
cor(SIMS~GRIP, data=data)
```

The correlation between SIMS and ARM in 0.69, while the correlation between SIMS and ARM is 0.64 so the correlation between SIMS and ARMS is greater. 

### Inferential Results 2
```{r}
model2 <- lm(SIMS~GRIP, data=data)
summary.lm(model2)
```

The adjusted R-squared value is 0.405, this is smaller than the SIMS vs ARM which was 0.471 and the p-value is very small.

```{r}
gripmod <- lm(SIMS~GRIP, data=data)
plot(SIMS~GRIP, data=data)
abline(gripmod)
summary.lm(gripmod)
```


### Model 3 SIMS~ARM+GRIP

```{r}
cor(SIMS~ARM,data=data)
cor(SIMS~GRIP,data=data)
cor(SIMS~ARM+GRIP,data=data)
```
Our correlation between SIMS and ARM/GRIP is 0.73.

### Inferential results 3 

```{r}
model3=lm(SIMS~ARM+GRIP,data=data)
summary.lm(model3)
```

OUR equation is SIMS = -5.43387 + 0.03731*ARM +0.02447*GRIP. This is the line in 3D space. 

```{r}
predict(model3,target,interval=c("prediction"))
```

```{r}
predict(model3,target,interval=c("confidence"))
```

The prediction interval for model3 is -2.2 to 2.4.The confidence interval is -0.23  to 0.48. 

### ANOVA tests
```{r}
anova(model1,model3)
```

```{r}
anova(model2,model3)
```


```{r}
anova(model1,model2)
```

Both Model1 and Model2 are nested with Model3. We can compare this by using an ANOVA test, as we get our results, we can see that we have low p values. If both models are not nested, then we cannot use the ANOVA test. 

