---
title: "Linear Model Prediction"
author: "Racheal Adeneye"
date: "2025-05-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
require(knitr)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt", sep="", header=TRUE)
```

### Model 1: SIMS~ARM
```{r}
basiccNN <- ggplot(data,aes(y=SIMS,x=ARM))
```

```{r}
basiccNN + geom_point() + ggtitle("SIMS vs ARM")
```

As we can see in the scatter plot for SIMS vs ARM above, we can see that the data is going uphill to the right. This relationship is a positive relationship.

### Numerical Results
```{r}
cor(SIMS~ARM, data=data)
```

The correlation between SIMS and ARM is 0.69.

### Inferential Results
```{r}
model1 <- lm(SIMS~ARM, data=data)
summary.lm(model1)
```

Out adjusted R-squared value is 0.467 and our p-value is extremely small.

### Target Dataframe
```{r}
target <- data.frame(ARM=90, GRIP=90)
```

```{r}
predict(model1, target, interval=c("prediction"))
```

The prediction interval goes from -1.6 to 3.2.

```{r}
predict(model1, target, interval=c("confidence"))
```

The confidence interval goes from 0.59 to 1.

### Model2 SIMS~GRIP
```{r}
basiccNN2 <- ggplot(data,aes(y=SIMS,x=GRIP))
```

```{r}
basiccNN2 + geom_point() + ggtitle("SIMS vs GRIP")
```

In this plot as well, we see that the data is going uphill and to the right. This relationship is a positive relationship.

### Numerical Results 2
```{r}
cor(SIMS~GRIP, data=data)
```

The correlation between SIMS and ARM in 0.69, while the correlation between SIMS and ARM is 0.64 so the correlation between SIMS and ARMS is greater. 

### Inferential Results 2
```{r}
model1 <- lm(SIMS~GRIP, data=data)
summary.lm(model1)
```